%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Publications}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\renewcommand{\section}[2]{} % hide the 'References' title of thebibliography
\begin{thebibliography}{aa}

\bibitem{Lusk2019} \textbf{P.\ C.\ Lusk}, K.\ Fathian, and J.\ P.\ How, ``CLIPPER: A Graph-Theoretic Framework for Robust Data Association,'' ICRA, 2021.

\bibitem{Lusk2019} \textbf{P.\ C.\ Lusk}, S.\ Wadhwania, X.\ Cai, A.\ Paris, K.\ Fathian, and J.\ P.\ How, ``A Distributed Pipeline for Visual-Inertial Formation Flying of Unmanned Aerial Vehicles,'' IROS, 2020.

\bibitem{Fathian2019} K.\ Fathian, K.\ Khosoussi, Y.\ Tian, \textbf{P.\ C.\ Lusk}, and J.\ P.\ How, ``CLEAR: A Consistent Lifting, Embedding, and Alignment Rectification Algorithm for Multi-View Data Association,'' (in review), 2019.

\bibitem{Lusk2019} \textbf{P.\ C.\ Lusk}, P.\ C.\ Glaab, L.\ J.\ Glaab and R.\ W.\ Beard, ``Safe2Ditch: Emergency Landing for Small Unmanned Aircraft Systems,'' \emph{AIAA Journal of Aerospace Information Systems}, 16(8), pp.\ 327-339, 2019.

\bibitem{Lee2018} J.\ H.\ Lee, J.\ D.\ Millard, \textbf{P.\ C.\ Lusk} and R.\ W.\ Beard, ``Autonomous target following with monocular camera on UAS using Recursive-RANSAC tracker,'' \emph{International Conference on Unmanned Aircraft Systems (ICUAS)}, Dallas, TX, pp. 1070-1074, 2018.

\bibitem{Lusk2018} \textbf{P.\ C.\ Lusk} and R.\ W.\ Beard, ``Visual Multiple Target Tracking from a Descending Aerial Platform,'' \emph{American Control Conference (ACC)}, Milwaukee, WI, pp. 5088–5093, 2018.

\end{thebibliography}